Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint Estimation

### 2015-04-10 2349-supp.tex
cam ready final

% \author{First Author\\
% Institution1\\
% Institution1 address\\
% {\tt\small firstauthor@i1.org}
% % For a paper whose authors are all at the same institution,
% % omit the following lines up until the closing ``}''.
% % Additional authors and addresses can be added with ``\and'',
% % just like the second author.
% % To save space, use either the email address or home page, not both
% \and
% Second Author\\
% Institution2\\
% First line of institution2 address\\
% {\tt\small secondauthor@i2.org}
% }

@@

%%%%%%%%% BODY TEXT
In the following, we present additional quantitative and qualitative
results that accompany the experiments described in Sect.~6 of the
main paper, ``Enriching Object Detection with 2D-3D Registration and
Continuous Viewpoint Estimation''.
% In Sect.~\ref{sec:3dobject}, we present detection result on qualitative results.

@@

We use $15\%$ context (extending the proposal region by $15\%$ on the
top, right, left, and bottom). We run our pipeline on the
PASCAL3D+~\cite{Xiang14} dataset, including our fine-tuning stage.
%
%If our method fails to estimate viewpoint (confidence score is below
%45), it
If our method fails to estimate viewpoint (confidence score is below a
threshold), it outputs 0 azimuth, 0 elevation, 0 yaw. Note that for
both categories and different numbers of viewpoints, our method has
difficulty distinguishing front and back views, but yields little
confusion between neighboring views. The failure cases given in
Fig.~\ref{fig:pascal3d_car_bad} and
Fig.~\ref{fig:pascal3d_bicycle_bad} are mostly caused by truncation,
occlusion, and unusual object shape.
%
\begin{figure*}[h]
  \centering
  \begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn8_crop.png}\\
    (a) Car, 4 views&
    (b) Car, 8 views\\
  \includegraphics[width=0.45\linewidth]{car_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn24_crop.png}\\
    (c) Car, 16 views&
    (d) Car, 24 views\\
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn8_crop.png}\\
    (e) Bicycle, 4 views&
    (j) Bicycle, 8 views\\  
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn24_crop.png}\\
    (g) Bicycle, 16 views&
    (h) Bicycle, 24 views\\
  \end{tabular}
  \caption{Detection and pose estimation on PASCAL3D+~\cite{Xiang14}
    cars and bicycles.
    Average Precision (red) and Average Viewpoint Precision (green)
    are given in the left plot and viewpoint confusion table and MPPE
    are given in the right plot. The viewpoint index 1 is front, 2 is
    front-right, \dots, $n-1$ is front-left for number of viewpoints $n$.}
 % On the left, we
 %  present average precision curve (red) average viewpoint precision curve
 %  (green). On the right, we present confusion matrix and mean precision in pose
 %  estimation. Viewpoint index 1 is front, index 2 is front-right \dots and
 %  $n-1$ is front-left for number of viewpoints $n$.}
  \label{fig:pascal_ap}
\end{figure*}
%
\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.24\linewidth]{supp/pas_aero1a.jpg} &
  \includegraphics[width=0.24\linewidth]{supp/pas_aero1b.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_aero2a.jpg} &
  \includegraphics[width=0.24\linewidth]{supp/pas_aero2b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_aero3a.jpg} &
  \includegraphics[width=0.24\linewidth]{supp/pas_aero3b.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_aero4a.jpg} &
  \includegraphics[width=0.24\linewidth]{supp/pas_aero4b.png} \\
  \hline
  \end{tabular}
  \caption{Successful detection and pose estimation results on
    PASCAL3D+~\cite{Xiang14} aeroplanes. Original image (left) and
  overlaid detection result (right). Proposal bounding box (blue) and
  predicted bounding box (purple).}
  \label{fig:pascal3d_aero_good}
\end{figure*}

@@

\section{Fine Tuning}
Lastly, we provide qualitative examples of the fine-tuning stage of
our pipeline based on MCMC sampling (Sect.~5 in the main paper) in
Fig.~\ref{fig:tuning}. Please note that, while the visual difference
appear subtle, our method often manages to improve upon the initial
pose estimate.
%
\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{ccc}
  \includegraphics[width=0.22\linewidth]{supp/tuning_1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_1c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_7a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_7b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_7c.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3c.png}  \\   
  \includegraphics[width=0.22\linewidth]{supp/tuning_4a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_4b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_4c.png}  \\     
  \includegraphics[width=0.22\linewidth]{supp/tuning_5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_5c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_6b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_6c.png}  \\
  \end{tabular}
\caption{Effect of fine-tuning based on MCMC sampling. From left to
  right: original image, initial pose estimate, and fine-tuned
  result. Numbers indicate detection confidence (s) and intersection
  over union (o), respectively.} 
  \label{fig:tuning}
\end{figure*}

>>>>

\author{Christopher Bongsoo Choy\textsuperscript{\dag}, Michael Stark\textsuperscript{\ddag}, Sam Corbett-Davies\textsuperscript{\dag}, Silvio Savarese\textsuperscript{\dag}\\
	\textsuperscript{\dag}Stanford University, \textsuperscript{\ddag}Max Planck Institute for Informatics\\
	{\tt\small \{chrischoy, scorbett, ssilvio\}@stanford.edu, \textsuperscript{\ddag}stark@mpi-inf.mpg.de }
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
% \author{First Author\\
% Institution1\\
% Institution1 address\\
% {\tt\small firstauthor@i1.org}
% % For a paper whose authors are all at the same institution,
% % omit the following lines up until the closing ``}''.
% % Additional authors and addresses can be added with ``\and'',
% % just like the second author.
% % To save space, use either the email address or home page, not both
% \and
% Second Author\\
% Institution2\\
% First line of institution2 address\\
% {\tt\small secondauthor@i2.org}
% }

@@

%%%%%%%%% BODY TEXT
In the following, we present additional quantitative and qualitative
results that accompany the experiments described in Sect.~6 of the
main paper, ``Enriching Object Detection with 2D-3D Registration and
Continuous Viewpoint Estimation''. \let\thefootnote\relax\footnote{Please visit \href{https://www.youtube.com/watch?v=YKtioOXY8yQ}{https://www.youtube.com/watch?v=YKtioOXY8yQ} for a biref summary of the paper and MCMC fine-tuning visualizations.}
% In Sect.~\ref{sec:3dobject}, we present detection result on qualitative results.

@@

We use $15\%$ context (extending the proposal region by $15\%$ on the
top, right, left, and bottom). We run our pipeline on the
PASCAL3D+~\cite{Xiang14} dataset, including our fine-tuning stage.
%
%If our method fails to estimate viewpoint (confidence score is below
%45), it
If our method fails to estimate viewpoint (confidence score is below a
threshold), it outputs 0 azimuth, 0 elevation, 0 yaw. Note that for
both categories and different numbers of viewpoints, our method has
difficulty distinguishing front and back views, but yields little
confusion between neighboring views. The failure cases given in
Fig.~\ref{fig:pascal3d_car_bad} and
Fig.~\ref{fig:pascal3d_bicycle_bad} are mostly caused by truncation,
occlusion, and unusual object shape.
%
\begin{figure*}[h]
  \centering
  \begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn8_crop.png}\\
    (a) Car, 4 views&
    (b) Car, 8 views\\
  \includegraphics[width=0.45\linewidth]{car_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn24_crop.png}\\
    (c) Car, 16 views&
    (d) Car, 24 views\\
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn8_crop.png}\\
    (e) Bicycle, 4 views&
    (j) Bicycle, 8 views\\  
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn24_crop.png}\\
    (g) Bicycle, 16 views&
    (h) Bicycle, 24 views\\
  \end{tabular}
  \caption{Detection and pose estimation on PASCAL3D+~\cite{Xiang14}
    cars and bicycles.
    Average Precision (red) and Average Viewpoint Precision (green)
    are given in the left plot and viewpoint confusion table and MPPE
    are given in the right plot. The viewpoint index 1 is front, 2 is
    front-right, \dots, $n-1$ is front-left for number of viewpoints $n$.}
 % On the left, we
 %  present average precision curve (red) average viewpoint precision curve
 %  (green). On the right, we present confusion matrix and mean precision in pose
 %  estimation. Viewpoint index 1 is front, index 2 is front-right \dots and
 %  $n-1$ is front-left for number of viewpoints $n$.}
  \label{fig:pascal_ap}
\end{figure*}

% \begin{figure*}[h]
% \setlength\tabcolsep{1pt}
% \centering
% \begin{tabular}{|cc|cc|}
%   \hline
%   \includegraphics[width=0.24\linewidth]{supp/pas_aero1a.jpg} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_aero1b.png} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_aero2a.jpg} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_aero2b.png} \\
%   \includegraphics[width=0.24\linewidth]{supp/pas_aero3a.jpg} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_aero3b.png} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_aero4a.jpg} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_aero4b.png} \\
%   \hline
%   \end{tabular}
%   \caption{Successful detection and pose estimation results on
%     PASCAL3D+~\cite{Xiang14} aeroplanes. Original image (left) and
%   overlaid detection result (right). Proposal bounding box (blue) and
%   predicted bounding box (purple).}
%   \label{fig:pascal3d_aero_good}
% \end{figure*}

@@

\section{Fine Tuning}
Lastly, we provide qualitative examples of the fine-tuning stage of
our pipeline based on MCMC sampling (Sect.~5 in the main paper) in
Fig.~\ref{fig:tuning}. Please note that, while the visual difference
appear subtle, our method often manages to improve upon the initial
pose estimate.
%
\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|ccc|}
	\hline
  \includegraphics[width=0.22\linewidth]{supp/tuning_1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_1c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_7a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_7b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_7c.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3c.png}  \\   
  \includegraphics[width=0.22\linewidth]{supp/tuning_4a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_4b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_4c.png}  \\     
  \includegraphics[width=0.22\linewidth]{supp/tuning_5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_5c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_6b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_6c.png}  \\
	\hline
  \end{tabular}
\caption{Effect of fine-tuning based on MCMC sampling. From left to
  right: original image, initial pose estimate, and fine-tuned
  result. Numbers indicate detection confidence (s) and intersection
  over union (o), respectively.} 
  \label{fig:tuning}
\end{figure*}

### 2015-04-10 2349.tex
cam ready final

\author{Christopher Bongsoo Choy\textsuperscript{\dag}, Michael Stark\textsuperscript{\dag \ddag}, Sam Corbett-Davies\textsuperscript{\dag}, Silvio Savarese\textsuperscript{\dag}\\
	\textsuperscript{\dag}Stanford University, \textsuperscript{\ddag}Max Planck Institute for Informatics\\
	{\tt\small \{chrischoy, scorbett, ssilvio\}@stanford.edu, \textsuperscript{\ddag}stark@mpi-inf.mpg.de }
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}

@@

\paragraph{Acknowledgement}
We acknowledge the support of NSF CAREER grant (N1054127), Ford-Stanford
Innovation Alliance Award, DARPA, Korea Foundation for Advanced Studies and
the Max Planck Center for Visual Computing \& Communication.

>>>>

\author{Christopher Bongsoo Choy\textsuperscript{\dag}, Michael Stark\textsuperscript{\ddag}, Sam Corbett-Davies\textsuperscript{\dag}, Silvio Savarese\textsuperscript{\dag}\\
	\textsuperscript{\dag}Stanford University, \textsuperscript{\ddag}Max Planck Institute for Informatics\\
	{\tt\small \{chrischoy, scorbett, ssilvio\}@stanford.edu, \textsuperscript{\ddag}stark@mpi-inf.mpg.de }
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}

@@

\paragraph{Acknowledgement}
We acknowledge the support of NSF CAREER grant (N1054127), Ford-Stanford
Innovation Alliance Award, DARPA, Fulbright New Zealand, Korea Foundation for
Advanced Studies and the Max Planck Center for Visual Computing \&
Communication.

### 2015-04-10 2349_ext.tex
cam ready final

\noindent
A large body of recent work on object detection has focused on providing more
information than a bounding box of an object. Some used 3D CAD
model databases to provide viewpoint estimation. These approaches work
by aligning exact 3D models to images using templates generated from renderings
of the 3D models at a set of discrete viewpoints~\cite{Aubry14}.

However, training the template for all viewpoint and CAD models is not feasible
since gathering all training data for different viewpoint and CAD models is
expensive.  Instead, it has been realized that template-based exemplar
detectors based on HOG features can be trained analytically, by
replacing the standard SVM with an LDA classifier $w_{x_t}$ for a template $x_t$
~\cite{Hariharan12}.

@@

Though generating and calibrating LDA templates (matrix decomposition with
Gaussian Elimination) achieved remarkable improvements, they are
computationally expensive and use a prohibitive amount of memory and storage.
In addition, viewpoint discretization hampers pose estimation performance.

@@

These components make template generation and evaluation computationally
inexpensive. Thus, we are able to efficiently explore the continuous parameter
space to find the best object pose, scale, 3D CAD model type and camera focal
length. The schematic of our pipeline is on Fig.~\ref{fig:front}.

Finally, our experimental study demonstrates the effectiveness of the
approach on several standard benchmarks for object detection and viewpoint
estimation. We also demonstrate that our method can enrich the output of an
existing object class detector, such as the DPM or the R-CNN with additional 3D
information.

@@

\vspace{-0.1in}
\paragraph{Non-Zero Whitened Histograms of Orientations.} Many works that use
rendering did not take the effect of background into account~\cite{Aubry14}
when synthesizing and whitening to generate an LDA template. Our NZ-WHO removes
background region while whitening thus it prevents irrelevant regions from
corrupting the foreground.

NZ-WHO method greatly speeds up the LDA generation. We introduced the Conjugate
Gradient method which runs in $O(n^2\kappa)$ time for LDA generation. Finally,
we experimentally show that our uncalibrated NZ-WHO template performs on par
with a calibrated WHO template but 100x faster to generate.

@@

We model the probability of an object with the parameter $\theta$ in the test
image $\mathcal{I}$ as $P(\theta| \mathcal{I}) \sim e^{ \max_{s} w(\theta)
	\ast \mathcal{T}_s(\mathcal{I})}$. We approximate the MAP solution for $p$ by
drawing samples from the distribution $P(\theta | \mathcal{I})$, using the
Metropolis-Hastings algorithm.

@@

Second, we demonstrate that our method can be used for multi-view
object class detection in isolation. It can be applied in a sliding
window fashion and deliver 2D bounding box as well as viewpoint
information. Our method is competitive with the state-of-the-art in this
case.

Finally, we show that our method can be used to complement the
detections provided by an existing object class detector, such
as DPM or RCNN. In this case, we show a considerable performance improvement
compared to previous work in the task of joint object class detection and VP
estimation. Example outputs of our model are on Fig.~\ref{fig:pascal12cnn}.

\vspace{-0.1in}
\paragraph{Acknowledgement.} We acknowledge the support of NSF CAREER grant
(N1054127), Ford-Stanford Innovation Alliance Award, DARPA, Korea Foundation
for Advanced Studies and the Max Planck Center for Visual Computing \&
Communication.

>>>>

\noindent
A large body of recent work on object detection has focused on providing more
information than the bounding box of an object. One set of methods use 3D CAD
model databases to provide viewpoint estimation. These approaches work
by aligning exact 3D models to images using templates generated from renderings
of the 3D models at a set of discrete viewpoints~\cite{Aubry14}.

However, training templates for all viewpoints and CAD models is not feasible
since it requires a huge amount of training data to be acquired. Instead, it has been realized that template-based exemplar
detectors based on HOG features can be trained analytically, by
replacing the standard SVM with an LDA classifier $w_{x_t}$ for a template $x_t$
~\cite{Hariharan12}.

@@

Though generating and calibrating LDA templates (via matrix decomposition with
Gaussian Elimination) achieved remarkable improvements, they are
computationally expensive and use a prohibitive amount of memory and storage.
In addition, viewpoint discretization hampers pose estimation performance.

@@

These components make template generation and evaluation computationally
inexpensive. Thus, we are able to efficiently explore the continuous parameter
space to find the best object pose, scale, 3D CAD model type and camera focal
length. An overview of our pipeline can be seen in Fig.~\ref{fig:front}.

Finally, our experimental study demonstrates the effectiveness of the
approach on several standard benchmarks for object detection and viewpoint
estimation. We also demonstrate that our method can enrich the output of an
existing object class detector, such as DPM or R-CNN, with additional 3D
information.

@@

\vspace{-0.1in}
\paragraph{Non-Zero Whitened Histograms of Orientations.} Many works that use
rendering do not take the background into account
when synthesizing and whitening to generate an LDA template~\cite{Aubry14}. Our NZ-WHO removes the
background region while whitening thus preventing irrelevant regions from
corrupting the foreground.

In addition, our NZ-WHO method uses Conjugate Gradient to greatly speeds up the LDA generation. We show that our uncalibrated NZ-WHO template performs on par
with a calibrated WHO template while being 100x faster to generate.

@@

We model the probability of an object with the parameter $\theta$ in the test
image $\mathcal{I}$ as $P(\theta| \mathcal{I}) \sim e^{ \max_{s} w(\theta)
	\ast \mathcal{T}_s(\mathcal{I})}$. We approximate the MAP solution for $\theta$ by
drawing samples from the distribution $P(\theta | \mathcal{I})$, using the
Metropolis-Hastings algorithm.

@@

Second, we demonstrate that our method can be used for multi-view
object class detection in isolation. It can be applied in a sliding
window fashion to deliver 2D bounding boxes and viewpoint
information. Our method is competitive with the state-of-the-art in this
case.

Finally, we show that our method can be used to complement the
detections provided by an existing object class detector, such
as DPM or R-CNN. In this case, we show a considerable performance improvement
compared to previous work in the task of joint object class detection and viewpoint
estimation. Example outputs of our model are in Fig.~\ref{fig:pascal12cnn}.

\vspace{-0.1in}
\paragraph{Acknowledgement.} We acknowledge the support of NSF CAREER grant
(N1054127), Ford-Stanford Innovation Alliance Award, DARPA, Korea Foundation
for Advanced Studies, Fulbright New Zealand and the Max Planck Center for Visual Computing \&
Communication.
